Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic

### 2021-10-25 psy_peds_3.Rmd
adding the code to save the outputs and remove the resampling bootstrap code

@@

>>>>

### ITS bootstrap

#### Parametric bootstrap

```{r}
bootstrap_size <- 1000
binom_proportion <- function(n, prob, size) {
  (rbinom(n, size, prob) / size) * 100
}
bootstrapped_timepoints <- mapply(binom_proportion,
                                  n = bootstrap_size,
                                  size = patient_count_psy_period_psy$count_no_psy_patients +
                                    patient_count_psy_period_psy$count_psy_patients,
                                  prob = patient_count_psy_period_psy$percentage/100)

bootstrapped_sample_list <- vector(mode = "list", length = bootstrap_size)
bootstrapped_coefficients_list <- vector(mode = "list", length = bootstrap_size)
for (iteration in 1:bootstrap_size) {
  df_iteration <- data.frame(period = patient_count_psy_period_psy$period,
                             time = patient_count_psy_period_psy$time,
                             percentage = bootstrapped_timepoints[iteration, ])
  ts_linear_percent <- lm(percentage ~ period * time, df_iteration)
  linear_model <- broom::tidy(ts_linear_percent) %>%
    filter(term %in% c("time", "periodduring_pandemic:time"))
  coefficients <- linear_model$estimate
  names(coefficients) <- linear_model$term
  bootstrapped_coefficients_list[[iteration]] <- coefficients
  df_iteration$predicted <- predict(ts_linear_percent)
  df_iteration$time_p <- patient_count_psy_period_psy$time_p
  bootstrapped_sample_list[[iteration]] <- df_iteration
}

bootstrapped_fitted_df <- bind_rows(bootstrapped_sample_list, .id = "iteration")

quantile_bootstrapped_fitted <- bootstrapped_fitted_df %>%
  group_by(time_p, period) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = quantile(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")

bootstrapped_coefficients_df <- bind_rows(bootstrapped_coefficients_list, .id = "iteration")
mean(bootstrapped_coefficients_df$time)
mean(bootstrapped_coefficients_df$time + bootstrapped_coefficients_df[["periodduring_pandemic:time"]])
pvalue_coeff_interaction <- round(t.test(bootstrapped_coefficients_df[["periodduring_pandemic:time"]])$p.value, 4)
pvalue_coeff_interaction <- ifelse(pvalue_coeff_interaction == 0,
                                   "< 1e-4",
                                   str(pvalue_coeff_interaction))
plot_annotation <- paste0("Diff. in slope coeffs before and after pandemic: ",
                     round(mean(bootstrapped_coefficients_df[["periodduring_pandemic:time"]]), 2),
                     " (pvalue: ",
                     pvalue_coeff_interaction,
                     ")")

# ggplot(bootstrapped_fitted_df, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
#   geom_line(aes(color = period),
#             alpha = 0.03) +
#   geom_line(data = quantile_bootstrapped_fitted,
#             aes(y = value, group = interaction(quantiles, period)),
#             linetype = "dashed") +
#   geom_line(data = quantile_bootstrapped_fitted[quantile_bootstrapped_fitted$quantiles == "50%", ],
#             aes(y = value, group = period)) +
#   geom_point(data = patient_count_psy_period_psy,
#              aes(y = percentage),
#              alpha = 0.5) +
#   scale_colour_manual(values = cbPalette) +
#   guides(color = guide_legend(override.aes = list(alpha = 1))) +
#   annotate("text",
#            x = as.Date("2019-10-01"),
#            y = max(patient_count_psy_period_psy[["percentage"]]) + 5,
#            label = annotation) +
#   labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
#        subtitle = "Parametric bootstrap estimation: (1000 iterations)",
#        x = "Calendar dates",
#        y = "Percentage",
#        color = "Period")

@@

# Save the output in a RData file. 
```{r}
#length_hospitalisation_values <- input_data %>% 
#  dplyr::distinct( patient_num, n_hospitalisation, len_hospitalisation ) %>%
#  dplyr::mutate( siteid = site ) %>%
#  dplyr::select( len_hospitalisation, siteid )
save( count_icd,
      patient_count_psy_period_psy,
      patient_count_psy_period_psy_clear,
      bootstrapped_coefficients_df,
      bootstrapped_fitted_df,
      perc_disorder_group,
      patients_hospitalized_agg_sex_perc,
      table1,
#      length_hospitalisation_values,
#      obs_by_day,
      file = paste0("output/peds_psy_aggResults_", unique(as.character(demo_raw$siteid)), ".RData"))
```
